### 2020-09-17 README.Rmd
updated talking points
updated talking points after meeting
added files for comparing random forest models to rtrees

## Talking points

**LIME**

**Graphics Group**

**Sandia**

## To Do List

- draft paper
- start organizing literature review paper
- set up dissertation R markdown document

## Oral Prelim

**Schedule**

- can be anytime during the semester 
- just needs to be 6 months before final defense
- schedule when it gets closer to the time 
- schedule 3 or 4 weeks in advance
- send prelim materials to committee 2 weeks in advance

**Materials**

- Chapter 0 (complete)
    - lit review
    - research statement: "this is what this thesis will investigate"
- Chatper 1 (as close to submission as possible)
    - LIME and shortcomings
    - Dr. Dixon likes to give feedback before submission
- Chapter 2 (draft)
    - Diagnostics for RF
- Chapter 3 (some idea)
    - Diagnostics for Bayesian Neural Networks
    - Could switch to chapter 2 if more complete
- Conclusion (not needed)

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-hamby_data_and_models`: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
- `02-understanding_lime`: explanation of LIME procedure
- `03-applying_lime`: applications of LIME to the models fit to the Hamby data
- `04-assessing_lime`: visual diagnostics for assessing the lime explanations
- `05-iris_comparison`: applying LIME to a random forest fit to the iris data
- `06-literature_review`: notes on papers relating to LIME
- `07-computation_issues`: documentation of some of the computation issues I ran into during the project

>>>>

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-hamby_data_and_models`: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
- `02-understanding_lime`: explanation of LIME procedure
- `03-applying_lime`: applications of LIME to the models fit to the Hamby data
- `04-assessing_lime`: visual diagnostics for assessing the lime explanations
- `05-iris_comparison`: applying LIME to a random forest fit to the iris data
- `06-literature_review`: notes on papers relating to LIME
- `07-computation_issues`: documentation of some of the computation issues I ran into during the project
- `08-logistic_regression`: examples of applying LIME to explain logistic regression models
- `09-refitting-rtrees`: examples where I retrain the rtrees model with the "current" version of the training data and compare the results
